Trends of downward SDR in Thessaloniki

### 2023-05-07 Article.Rmd
Commit 2023-05-07 21:17

<!-- measurement -->
The signal of the CM-21 pyranometer is sampled with a rate of $1 {Hz}$, and a record the average signal and the standard deviation every one minute is recorded.
<!-- dark correction -->
The measurements are corrected for the zero offset of the instrument, using the "dark signal" (Sun elevation bellow $10^\circ$, for a period of $3 h$).
<!-- physical quantities -->
The signal is converted to radiation using a ramped value of the instrument sensitivity, derived from the eight laboratory calibrations of the instrument, during the study period.

>>>>

<!-- measurement -->
The signal of the CM-21 pyranometer is sampled with a rate of $1 {Hz}$, and a record the average signal and the standard deviation every one minute is recorded.
<!-- dark correction -->
The measurements are corrected for the zero offset of the instrument, using the "dark signal" (Sun elevation angle bellow $-10^\circ$, for a period of $3 h$).
<!-- physical quantities -->
The signal is converted to radiation using a ramped value of the instrument sensitivity, derived from the eight laboratory calibrations of the instrument, during the study period.
